Sample-Efficient Reinforcement Learning \\ with Implicitly Quantized Representations

### 2024-02-02 paper/main.tex
updated abstract

\begin{abstract}
  In reinforcement learning (RL) for continuous control, we propose an
  efficient representation learning method using only a latent-state
  consistency loss. Our approach employs an encoder and a transition
  model to map observations to latent states and predict future
  states, respectively. We achieve high performance and prevent
  representation collapse by normalizing the quantized latent
  representation such that rank in the presentation is empirically
  preserved. Our method is straightforward, compatible with any
  model-free RL algorithm, and demonstrates state-of-the-art
  performance in continuous control benchmarks from DeepMind Control
  Suite.
\end{abstract}

>>>>

\begin{abstract}
  Learning representations for reinforcement learning (RL) has shown much promise for continuous control. We propose an efficient representation learning method using only a self-supervised latent-state consistency loss. Our approach employs an encoder and a transition model to map observations to latent states and predict future states, respectively. We achieve high performance and prevent representation collapse by normalizing and bounding the latent representation such that rank in the representation is empirically preserved. Our method is straightforward, compatible with any model-free RL algorithm, and demonstrates state-of-the-art performance in continuous control benchmarks from DeepMind Control Suite.
\end{abstract}

% \begin{abstract}
%   In reinforcement learning (RL) for continuous control, we propose an
%   efficient representation learning method using only a latent-state
%   consistency loss. Our approach employs an encoder and a transition
%   model to map observations to latent states and predict future
%   states, respectively. We achieve high performance and prevent
%   representation collapse by normalizing the quantized latent
%   representation such that rank in the presentation is empirically
%   preserved. Our method is straightforward, compatible with any
%   model-free RL algorithm, and demonstrates state-of-the-art
%   performance in continuous control benchmarks from DeepMind Control
%   Suite.
% \end{abstract}
